Human Capital Model

### 2016-02-01 Tex/paper.tex
123

\begin{itemize}
\item \textbf{assumption 1} If an employee has probability to
  promote, he won't churn.

The possibility of the unforeseen accidents, which could force an
employee to leave his position,is neglected.Human nature, an employee
will stay at his position to chase for higher level.

\item \textbf{assumption 2} For a vacancy,if there exists an
  employee measures up to it already,ICM won't recruit for it.

Since recruiting good people is difficult, time consuming and
expensive according to issue 5,it is wasteful to recruit for a
position if an employee can promote to it.

\item \textbf{assumption 3} Demotion won't occur.

\item \textbf{assumption 4} Administrative clerk won't promote or be
  transferred.

>>>>

\begin{itemize}
\item \textbf{assumption 1} The surface temperature of bathtub and the person keeps constant.

    Since human-being is temperature-constant, and bathtub contacts the ground, we can assume that they have no heat exchange.

\item \textbf{assumption 2} The volume of water flowing away is equivalent to that of hot water at any time.

    Although water has evaporation loss and other kinds of losses,  it takes up a small proportion of the total volume. Thus we sensibly neglect them.

\item \textbf{assumption 3} The hot water from the faucet has a constant flow velocity and temperature.

\item \textbf{assumption 4} There is no convection in the water.

The temperature water in the bathtub is a relatively
